---
title: "Initial model ideas"
author: "Colin Millar"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    keep_tex: no
---



```{r}
cars <- list(x = 1:10, y = 1:10)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

# Capture probability model

The capture probability model is based on the framework developed by Huggins and Yip (1997). Let $n_{ijk}$ be the number of fish of life-stage $j$ caught on pass $k$ in sample $i$, $i = 1,\ldots, N$, $j = 1, 2$ (fry, parr respectively), $k = 1, 2, 3$. Further, let $p_{ijk}$ be the corresponding capture probability, assumed by necessity to be common across individuals within samples, life stages and passes because length information is not available. The log-likelihood of the data is then (subject to an additive constant):

$$L_{ij} = \prod{ij} \frac{p_{ij1}^{n_{ij1}} \left(q_{ij1} p_{ij2}\right)^{n_{ij2}} \left(q_{ij1}q_{ij2}p_{ij3}\right)^{n_{ij3}}} {\left(p_{ij1} + q_{ij1}p_{ij2} + q_{ij1}q_{ij2}p_{ij3}\right)^{n_{ij.}}}$$

where $q_{ijk} = 1 - p_{ijk}$ and $n_{ij.} = n_{ij1} + n_{ij2} + n_{ij3}$. This model is over-parameterised so constraints are imposed by assuming that the capture probabilities are a linear logistic function of explanatory variables $x_l$, $l = 1, \ldots, M$. That is:

$$\text{logit} p_{ijk} = \beta_0 + \sum_{l} \beta_l x_{ijkl}$$

where $x_{ijkl}$ is the value of $x_l$ for sample $i$, life-stage $j$ and pass $k$, and $\beta_0$ and $\beta_l$, $l = 1, \ldots, M$, are parameters to be estimated. Although the use of linear logistic models may appear limiting, the formulation above can incorporate categorical variables, interactions, smoothing splines with fixed degrees of freedom and spatial models (Yee and Hastie, 2003). 

